rough outline

### 2022-04-29 population_data.Rmd
Joined dataframe

edit
```

>>>>

edit
```
```{r}
country_deaths <- deaths_df %>% 
    filter(country %in% c('Canada', 'Argentina', 'Seychelles', 'Romania', 
                          'Israel', 'Tonga','United States', 'Brazil', 
                          'Ethiopia', 'Russia', 'China', 'Australia'))

#joined_country_pop <- full_join(country_deaths, edit, by = c("country" = "Country.Name"))
#glimpse(joined_country_pop)
#head(joined_country_pop, 15)

joined_country_pop <- full_join(country_deaths, edit, by = c("country" = "Country.Name"))
```
